### 2023-06-20 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
working on figs
revised Fig 3

\begin{figure}[H]
  \centering
%  \input{figures/concModels.tikz} \\
  \subfigimg[width=0.9\linewidth, clip ]{(a)}{figures/oldbending.pdf} \\
  \subfigimg[width=0.9\linewidth, clip ]{(b)}{figures/concModels.pdf}
  \caption{\label{fig:concModels} \small (a) A multicomponent vesicle
  entering a closely-fitting channel using the linear
  model~\eqref{eqn:linearBending}. The vesicle bending modulus becomes
  negative, and this introduces an instability that first appears near
  the point with the largest negative curvature. (b) The linear bending
  model in red (equation~\eqref{eqn:linearBending}) and the new
  hyperbolic bending model in blue (equation~\eqref{eqn:tanhBending}).
  Note that the new bending model satisfies $b \in (\beta,1)$ even if $u
  \notin [0,1]$.}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Validation}
\label{sec:validation}
We validate the new bending model~\eqref{eqn:tanhBending} by reproducing
the tank treading and phase treading dynamics reported in the
literature. Figure~\ref{fig:treading} shows a tank treading (top) and a
phase treading (bottom) multicomponent vesicle in an unconfined shear
flow. These simulations align with the results reported
by~\citet{liu-mar-li-vee-low2017} (cf.~Figures 3 and 4).
\begin{figure}[H]
  \todo[inline]{Change to new color scheme.}
  \centering
  \subfigimg[width=\columnwidth, trim ={5.5cm 1.5cm 4cm 0},clip]{(a)}{figures/Fig4a.pdf}
  \subfigimg[width=\columnwidth, trim ={5.5cm 1.5cm 4cm 0},clip]{(b)}{figures/Fig4b.pdf}
  \caption{\label{fig:treading} \small A multicomponent (a)
  tank-treading and (b) phase-treading vesicle using the new bending
  model~\eqref{eqn:tanhBending}. These simulations agree with the
  results presented by~\citet{liu-mar-li-vee-low2017}.}
\end{figure}

@@

The lubrication layer between a vesicle and the solid wall plays a
critical role on the vesicle's dynamics. Therefore, throughout
Section~\ref{sec:results}, we will calculate the size and analyze the
flow structure inside the lubrication layers. 
%We first justify the use of the term `lubrication layer' by verifying
%that the flow velocity is parabolic between the vesicle and the solid
%wall. Figure~\ref{fig:quadraticProof} illustrates the horizontal
%velocity (solid line) and the corresponding best fit quadratic (dashed
%line) in the co-moving frame, and the profiles agree.
%
%\begin{figure}[H]
%    \centering
%    \includegraphics[width=\columnwidth]{figures/lubricationLayer_quadratic.pdf}  
%    \caption{The co-moving velocity profile in the top and bottom lubrication layers. The red curve is the velocity profile, the dashed black line is the best quadratic fit.}
%    \label{fig:quadraticProof}
%\end{figure}
To define the size of the top lubrication layer (the size of the bottom
lubrication layer is defined similarly), we let
$d(\xx,\Gamma_\mathrm{top})$ be the minimum distance between the vesicle
and the top half of the confining geometry.
%\begin{align}
%    d(\xx,\Gamma_\mathrm{top}) = \inf_{\yy \in \Gamma_\mathrm{top}} \|\xx-\yy\|,
%\end{align}
%where $\Gamma_{\mathrm{top}}$ is the top portion of $\Gamma$.
We then find all local minimums of $d(\xx,\Gamma_\mathrm{top})$, with
the condition that $d(\xx,\Gamma_\mathrm{top}) < \beta$, where $\beta$
is a parameter. If no such local minimums exist, then the vesicle is too
far from $\Gamma_\mathrm{top}$ to define a lubrication layer. If there
are two or more local minimums, the left-most, $\xx_L$, and right-most,
$\xx_R$, local minimums form the start and end of the lubrication layer.
If there is only one local minimum, then $\xx_L$ and $\xx_R$ are the
points on $\gamma$ to the left and right of this local minimum with the
condition that $d(\xx_L,\Gamma_\mathrm{top}) =
d(\xx_R,\Gamma_\mathrm{top}) = \beta$. Then, the segment
$\gamma_{\mathrm{layer}} \subset \gamma$ consists of all points $\xx \in
\gamma$ between $\xx_L$ and $\xx_R$ with the condition that
$d(\xx,\Gamma_\mathrm{top}) < \beta$. Finally, the lubrication layer
width is
\begin{align}
    w_\mathrm{top} = \frac{1}{|\gamma_{_\mathrm{layer}}|} \int_{\gamma_{_\mathrm{layer}}} d(\xx,\Gamma_\mathrm{top}) \, ds.
\end{align}
The width of the bottom lubrication layer, $w_\mathrm{bot}$ is calculated replacing $\Gamma_\mathrm{top}$ with $\Gamma_\mathrm{bot}$.

@@

The difference between the size of the top and lubrication layers is closely related to the tank treading behavior of the vesicle. In cases where the vesicle tank treads, we define the tank-treading velocity, $\uu \cdot \ss$. To establish that a vesicle is tank treading, we compute this tangential velocity at several Lagrangian points on $\gamma$, and make sure that these values agree.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We consider both a single-component and a multicomponent vesicle suspended in two geometries: a closely-fitting geometry (stenosis) and a geometry that slowly contracts to a narrow neck and then quickly widens (contracting). We considered a semipermeable vesicle suspended in these same geometries~\cite{qua-gan-you2021}. All the multicomponent examples have the bending ratio $b_{\min}/b_{\max} = 10^{-1}$. For the single-component case, we consider two dimensionless bending stiffness: $b(u) = b_{\max} = 1$ and $b(u) = \frac{1}{2}(b_{\max} + b_{\min}) = 0.55$. Throughout this section we plot the position of the vesicle in terms of the $x$-coordinate of its center of mass. For the stenosed geometry in Section~\ref{subsec:Stenosis}, the narrow region begins at $x=-15$ and ends at $x=15$. For the contracting geometry in Section~\ref{subsec:Contraction}, the geometry begins to narrow at $x=4$ and reaches its narrowest point at $x=15$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{subsec:Stenosis}A multicomponent vesicle in a closely-fit channel (Stenosis)}

>>>>

\begin{figure}[H]
  \centering
%  \input{figures/concModels.tikz} \\
%  \subfigimg[width=0.9\linewidth, clip ]{(a)}{figures/oldbending.pdf} \\
  \subfigimg[width=0.9\linewidth, clip ]{(a)}{figures/OldBending.pdf} \\
  \subfigimg[width=0.9\linewidth, clip ]{(b)}{figures/concModels.pdf}
  \caption{\label{fig:concModels} \small (a) A multicomponent vesicle
  entering a closely-fitting channel using the linear
  model~\eqref{eqn:linearBending}. The vesicle bending modulus becomes
  negative, and this introduces an instability that first appears near
  the point with the largest negative curvature. (b) The linear bending
  model in red (equation~\eqref{eqn:linearBending}) and the new
  hyperbolic bending model in blue (equation~\eqref{eqn:tanhBending}).
  Note that the new bending model satisfies $b \in (\beta,1)$ even if $u
  \notin [0,1]$.}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Validation}
\label{sec:validation}
We validate the new bending model~\eqref{eqn:tanhBending} by reproducing
the tank treading and phase treading dynamics reported in the
literature. Figure~\ref{fig:treading} shows a tank treading (top) and a
phase treading (bottom) multicomponent vesicle in an unconfined shear
flow. These simulations align with the results reported
by~\citet{liu-mar-li-vee-low2017} (cf.~Figures 3 and 4).
\begin{figure}[H]
  \todo[inline]{Change to new color scheme.}
  \centering
  \includegraphics[width=0.9\columnwidth]{figures/shearTreading.pdf}
%  \subfigimg[width=\columnwidth, trim ={5.5cm 1.5cm 4cm 0},clip]{(a)}{figures/Fig4a.pdf}
%  \subfigimg[width=\columnwidth, trim ={5.5cm 1.5cm 4cm 0},clip]{(b)}{figures/Fig4b.pdf}
  \caption{\label{fig:treading} \small A multicomponent vesicle in a
  linear shear flow undergoes phase-treading (top) and tank-treading
  (bottom) with the new bending model~\eqref{eqn:tanhBending}. The red
  region is stiff and the blue region is floppy. The simulations
  qualitatively agree with the results presented
  by~\citet{liu-mar-li-vee-low2017}.}
\end{figure}

@@

The lubrication layer between a vesicle and the solid wall plays a
critical role on the vesicle's dynamics. Therefore, throughout
Section~\ref{sec:results}, we will calculate the size and analyze the
flow structure inside the lubrication layers. 
%We first justify the use of the term `lubrication layer' by verifying
%that the flow velocity is parabolic between the vesicle and the solid
%wall. Figure~\ref{fig:quadraticProof} illustrates the horizontal
%velocity (solid line) and the corresponding best fit quadratic (dashed
%line) in the co-moving frame, and the profiles agree.
%
%\begin{figure}[H]
%    \centering
%    \includegraphics[width=\columnwidth]{figures/lubricationLayer_quadratic.pdf}  
%    \caption{The co-moving velocity profile in the top and bottom lubrication layers. The red curve is the velocity profile, the dashed black line is the best quadratic fit.}
%    \label{fig:quadraticProof}
%\end{figure}
To define the size of the top lubrication layer (the size of the bottom
lubrication layer is defined similarly), we let
$d(\xx,\Gamma_\mathrm{top})$ be the minimum distance between the vesicle
and the top half of the confining geometry.
%\begin{align}
%    d(\xx,\Gamma_\mathrm{top}) = \inf_{\yy \in \Gamma_\mathrm{top}} \|\xx-\yy\|,
%\end{align}
%where $\Gamma_{\mathrm{top}}$ is the top portion of $\Gamma$.
We then find all local minimums of $d(\xx,\Gamma_\mathrm{top})$, with
the condition that $d(\xx,\Gamma_\mathrm{top}) < \beta$, where $\beta$
is a parameter. If no such local minimums exist, then the vesicle is too
far from $\Gamma_\mathrm{top}$ to define a lubrication layer. If there
are two or more local minimums, the left-most, $\xx_L$, and right-most,
$\xx_R$, local minimums form the start and end of the lubrication layer.
If there is only one local minimum, then $\xx_L$ and $\xx_R$ are the
points on $\gamma$ to the left and right of this local minimum with the
condition that $d(\xx_L,\Gamma_\mathrm{top}) =
d(\xx_R,\Gamma_\mathrm{top}) = \beta$. Then, the segment
$\gamma_{\mathrm{layer}} \subset \gamma$ consists of all points $\xx \in
\gamma$ between $\xx_L$ and $\xx_R$ with the condition that
$d(\xx,\Gamma_\mathrm{top}) < \beta$. Finally, the lubrication layer
width is
\begin{align}
    w_\mathrm{top} = \frac{1}{|\gamma_{_\mathrm{layer}}|} \int_{\gamma_{_\mathrm{layer}}} d(\xx,\Gamma_\mathrm{top}) \, ds.
\end{align}
The width of the bottom lubrication layer, $w_\mathrm{bot}$ is
calculated by replacing $\Gamma_\mathrm{top}$ with
$\Gamma_\mathrm{bot}$.

@@

The difference between the size of the top and lubrication layers is
closely related to the tank treading behavior of the vesicle. In cases
where the vesicle tank treads, we define the tank-treading velocity,
$\uu \cdot \ss$. To establish that a vesicle is tank treading, we verify
that the tangential velocity agrees at several points on $\gamma$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider both a single-component and a multicomponent vesicle
suspended in two geometries: a closely-fitting geometry (stenosis) and a
geometry that slowly contracts to a narrow neck and then quickly widens
(contracting). We considered a semipermeable vesicle suspended in these
same geometries~\cite{qua-gan-you2021}. All the multicomponent examples
have the bending ratio $b_{\min}/b_{\max} = 10^{-1}$. For the
single-component case, we consider two dimensionless bending stiffness:
$b(u) = b_{\max} = 1$ and $b(u) = \frac{1}{2}(b_{\max} + b_{\min}) =
0.55$. Throughout this section we plot the position of the vesicle in
terms of the $x$-coordinate of its center of mass. For the stenosed
geometry in Section~\ref{subsec:Stenosis}, the narrow region begins at
$x=-15$ and ends at $x=15$. For the contracting geometry in
Section~\ref{subsec:Contraction}, the geometry begins to narrow at $x=4$
and reaches its narrowest point at $x=15$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{subsec:Stenosis}A multicomponent vesicle in a closely-fit channel (Stenosis)}
